peter_models

### 2025-01-09 RQ1_Analysis/peter_EDA.qmd

| **Variable** | **Level** | **Count** | **Proportion** |
|------------------|-------------------|------------------|------------------|
| Q29 | \(1\) Very interested in politics | 4306 | 25% |
| Q29 | \(2\) Somewhat interested | 7612 | 43% |
| Q29 | \(3\) Not that interested in politics | 3643 | 21% |
| Q29 | \(4\) Not at all interested in politics | 1984 | 11% |
| Q271 | \(1\) Extremely important | 5487 | 31% |
| Q271 | \(2\) Very important | 4330 | 25% |
| Q271 | \(3\) Moderately important | 3754 | 21% |
| Q271 | \(4\) Slightly important | 1505 | 9% |
| Q271 | \(5\) Not at all important | 2469 | 14% |
| S2_RACE_PRIME | \(1\) White | 3923 | 22% |
| S2_RACE_PRIME | \(2\) Hispanic or Latino | 3873 | 22% |
| S2_RACE_PRIME | \(3\) Black or African American | 4613 | 26% |
| S2_RACE_PRIME | \(4\) Asian American | 3826 | 22% |
| S2_RACE_PRIME | \(5\) American Indian/Native American | 713 | 4% |
| S2_RACE_PRIME | \(6\) Arab, Middle Eastern or North African | 226 | 1% |
| S2_RACE_PRIME | \(7\) Native Hawaiian | 106 | 1% |
| S2_RACE_PRIME | \(8\) Not Hawaiian, but other Pacific Islander | 255 | 1% |
| S3 | \(01\) Straight, that is, not gay or lesbian | 15404 | 88% |
| S3 | \(02\) Gay or lesbian | 594 | 3% |
| S3 | \(03\) Bisexual | 937 | 5% |
| S3 | \(04\) Something else (Specify) | 286 | 2% |
| S3 | \(88\) Refused | 195 | 1% |
| S3 | \(99\) I don | 129 | 1% |
| S3B | \(1\) Man | 7431 | 42% |
| S3B | \(2\) Woman | 9932 | 57% |
| S3B | \(3\) Non-binary | 148 | 1% |
| S3B | \(4\) Something else (Specify) | 34 | 0% |
| S5_AGE | \(2\) 18-29 | 4026 | 23% |
| S5_AGE | \(3\) 30-39 | 3614 | 21% |
| S5_AGE | \(4\) 40-49 | 2783 | 16% |
| S5_AGE | \(5\) 50-59 | 2717 | 15% |
| S5_AGE | \(6\) 60-69 | 2745 | 16% |
| S5_AGE | \(7\) 70 + | 1660 | 9% |
| S13 | \(1\) Grades 1-8 | 126 | 1% |
| S13 | \(2\) Some High School, but did not graduate | 596 | 3% |
| S13 | \(3\) High School graduate or GED | 3227 | 18% |
| S13 | \(4\) Some college | 3689 | 21% |
| S13 | \(5\) Associates, 2-year degree | 2017 | 12% |
| S13 | \(6\) Bachelors, 4-year degree | 4625 | 26% |
| S13 | \(7\) Post-graduate degree | 3265 | 19% |
| S7 | \(1\) United States | 13297 | 76% |
| S7 | \(2\) Another country | 3962 | 23% |
| S7 | \(3\) on the Island of Puerto Rico | 286 | 2% |
| Q21 | \(1\) Republican | 3238 | 18% |
| Q21 | \(2\) Democrat | 8318 | 47% |
| Q21 | \(3\) Independent | 5174 | 29% |
| Q21 | \(4\) Other party | 815 | 5% |
| S2_M | \(1\) Yes | 4671 | 27% |
| S2_M | \(2\) No | 12874 | 73% |
| Q627 | \(1\) Yes | 8365 | 48% |
| Q627 | \(2\) No | 9180 | 52% |
| Q628 | \(1\) In the United States | 1404 | 76% |
| Q628 | \(2\) In my country of origin | 153 | 8% |
| Q628 | \(3\) In both places | 279 | 15% |
| Q629R1 | \(0\) NO TO: Racial background or ethnicity | 2947 | 35% |
| Q629R1 | \(1\) Racial background or ethnicity | 5418 | 65% |
| Religion | Catholic | 3702 | 21% |
| Religion | Protestant | 4045 | 23% |
| Religion | Other Christian | 1826 | 10% |
| Religion | Jewish | 264 | 2% |
| Religion | Muslim | 524 | 3% |
| Religion | Hindu | 491 | 3% |
| Religion | Buddhist | 464 | 3% |
| Religion | Mormon/LDS | 112 | 1% |
| Religion | Folk Religion | 27 | 0% |
| Religion | Daoist | 21 | 0% |
| Religion | Shamanism | 26 | 0% |
| Religion | Ancestral Religion | 77 | 0% |
| Religion | Spiritual but not religious | 1288 | 7% |
| Religion | Atheist | 820 | 5% |
| Religion | Agnostic | 1084 | 6% |
| Religion | None | 2774 | 16% |
| educ | College graduate | 9907 | 56% |
| educ | No college experience | 3949 | 23% |
| educ | Some college experience | 3689 | 21% |
| sex_orientaton | Queer | 1817 | 10% |
| sex_orientation | Refused/Don't Know | 324 | 2% |
| sex_orientation | Straight | 15404 | 88% |
| rural | Rural | 1453 | 8% |
| rural | Urban/suburban | 16092 | 92% |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |

>>>>

| **Variable** | **Level** | **Count** | **Proportion** |
|----|----|----|----|
| Q29 | \(1\) Very interested in politics | 4306 | 25% |
| Q29 | \(2\) Somewhat interested | 7612 | 43% |
| Q29 | \(3\) Not that interested in politics | 3643 | 21% |
| Q29 | \(4\) Not at all interested in politics | 1984 | 11% |
| Q271 | \(1\) Extremely important | 5487 | 31% |
| Q271 | \(2\) Very important | 4330 | 25% |
| Q271 | \(3\) Moderately important | 3754 | 21% |
| Q271 | \(4\) Slightly important | 1505 | 9% |
| Q271 | \(5\) Not at all important | 2469 | 14% |
| S2_RACE_PRIME | \(1\) White | 3923 | 22% |
| S2_RACE_PRIME | \(2\) Hispanic or Latino | 3873 | 22% |
| S2_RACE_PRIME | \(3\) Black or African American | 4613 | 26% |
| S2_RACE_PRIME | \(4\) Asian American | 3826 | 22% |
| S2_RACE_PRIME | \(5\) American Indian/Native American | 713 | 4% |
| S2_RACE_PRIME | \(6\) Arab, Middle Eastern or North African | 226 | 1% |
| S2_RACE_PRIME | \(7\) Native Hawaiian | 106 | 1% |
| S2_RACE_PRIME | \(8\) Not Hawaiian, but other Pacific Islander | 255 | 1% |
| S3 | \(01\) Straight, that is, not gay or lesbian | 15404 | 88% |
| S3 | \(02\) Gay or lesbian | 594 | 3% |
| S3 | \(03\) Bisexual | 937 | 5% |
| S3 | \(04\) Something else (Specify) | 286 | 2% |
| S3 | \(88\) Refused | 195 | 1% |
| S3 | \(99\) I don | 129 | 1% |
| S3B | \(1\) Man | 7431 | 42% |
| S3B | \(2\) Woman | 9932 | 57% |
| S3B | \(3\) Non-binary | 148 | 1% |
| S3B | \(4\) Something else (Specify) | 34 | 0% |
| S5_AGE | \(2\) 18-29 | 4026 | 23% |
| S5_AGE | \(3\) 30-39 | 3614 | 21% |
| S5_AGE | \(4\) 40-49 | 2783 | 16% |
| S5_AGE | \(5\) 50-59 | 2717 | 15% |
| S5_AGE | \(6\) 60-69 | 2745 | 16% |
| S5_AGE | \(7\) 70 + | 1660 | 9% |
| S13 | \(1\) Grades 1-8 | 126 | 1% |
| S13 | \(2\) Some High School, but did not graduate | 596 | 3% |
| S13 | \(3\) High School graduate or GED | 3227 | 18% |
| S13 | \(4\) Some college | 3689 | 21% |
| S13 | \(5\) Associates, 2-year degree | 2017 | 12% |
| S13 | \(6\) Bachelors, 4-year degree | 4625 | 26% |
| S13 | \(7\) Post-graduate degree | 3265 | 19% |
| S7 | \(1\) United States | 13297 | 76% |
| S7 | \(2\) Another country | 3962 | 23% |
| S7 | \(3\) on the Island of Puerto Rico | 286 | 2% |
| Q21 | \(1\) Republican | 3238 | 18% |
| Q21 | \(2\) Democrat | 8318 | 47% |
| Q21 | \(3\) Independent | 5174 | 29% |
| Q21 | \(4\) Other party | 815 | 5% |
| S2_M | \(1\) Yes | 4671 | 27% |
| S2_M | \(2\) No | 12874 | 73% |
| Q627 | \(1\) Yes | 8365 | 48% |
| Q627 | \(2\) No | 9180 | 52% |
| Q628 | \(1\) In the United States | 1404 | 76% |
| Q628 | \(2\) In my country of origin | 153 | 8% |
| Q628 | \(3\) In both places | 279 | 15% |
| Q629R1 | \(0\) NO TO: Racial background or ethnicity | 2947 | 35% |
| Q629R1 | \(1\) Racial background or ethnicity | 5418 | 65% |
| Religion | Catholic | 3702 | 21% |
| Religion | Protestant | 4045 | 23% |
| Religion | Other Christian | 1826 | 10% |
| Religion | Jewish | 264 | 2% |
| Religion | Muslim | 524 | 3% |
| Religion | Hindu | 491 | 3% |
| Religion | Buddhist | 464 | 3% |
| Religion | Mormon/LDS | 112 | 1% |
| Religion | Folk Religion | 27 | 0% |
| Religion | Daoist | 21 | 0% |
| Religion | Shamanism | 26 | 0% |
| Religion | Ancestral Religion | 77 | 0% |
| Religion | Spiritual but not religious | 1288 | 7% |
| Religion | Atheist | 820 | 5% |
| Religion | Agnostic | 1084 | 6% |
| Religion | None | 2774 | 16% |
| educ | College graduate | 9907 | 56% |
| educ | No college experience | 3949 | 23% |
| educ | Some college experience | 3689 | 21% |
| sex_orientaton | Queer | 1817 | 10% |
| sex_orientation | Refused/Don't Know | 324 | 2% |
| sex_orientation | Straight | 15404 | 88% |
| rural | Rural | 1453 | 8% |
| rural | Urban/suburban | 16092 | 92% |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |
|  |  |  |  |

### 2025-01-09 RQ1_Analysis/peter_models.qmd

>>>>

### TESTING PLOT

```{r}
  or_data <- exp(cbind(OR = coef(ord_mod_interactions), confint(ord_mod_interactions)))

  # Calculate p-values
  p_values <- pnorm(-abs(summary(ord_mod_interactions)$coefficients[, "t value"])) * 2

  # Keep only significant variables
  sig_indices <- p_values[names(coef(ord_mod_interactions))] < 0.05
  or_data_sig <- or_data[sig_indices, ]

  # Create a mapping for variable names with grouping prefixes
  rename_map <- c(
    # Education Group
    "educCollege graduate" = "1. Education: College Graduate",
    "educSome college experience" = "1. Education: Some College",

    # Gender Group
    "S3B(2) Woman" = "2. Gender: Woman",
    "S3B(3) Non-binary" = "2. Gender: Non-binary",

    # Age Group
    "age_recoded70+" = "3. Age: 70+",
    "age_recoded60-69" = "3. Age: 60-69",
    "age_recoded50-59" = "3. Age: 50-59",

    # Race Group
    "race_recodedBlack" = "4. Race: Black",
    "race_recodedAsian American" = "4. Race: Asian",
    "race_recodedLatino" = "4. Race: Latino",
    "race_recodedAIAN" = "4. Race: Native",
    "race_recodedNHPI" = "4. Race: NHPI",

    # Racial Belonging Group
    "Q271_reordered(2) Very important" = "5. Racial Belonging: Very Important",
    "Q271_reordered(1) Extremely important" = "5. Racial Belonging: Extremely Important",

    # Party ID Group
    "Q21(2) Democrat" = "6. Party ID: Democrat",
    "Q21(3) Independent" = "6. Party ID: Independent",
    "Q21(4) Other party" = "6. Party ID: Other",

    # Interactions
    "Q271_reordered(1) Extremely important:S3B(2) Woman" = "7. Interaction: Racial Belonging & Gender: Woman"
  )

  # Rename the rownames in the significant data
  or_data_sig_renamed <- as.data.frame(or_data_sig)  # Ensure this is a data frame
  rownames(or_data_sig_renamed) <- rename_map[rownames(or_data_sig_renamed)]

  # Create a custom grouping variable based on the row names
  group_labels <- c(
    "Racial Belonging" = "5. Racial Belonging: Very Important", 
    "Racial Belonging" = "5. Racial Belonging: Extremely Important",
    "Gender" = "2. Gender: Woman", 
    "Gender" = "2. Gender: Non-binary", 
    "Race" = "4. Race: Black", 
    "Race" = "4. Race: Asian", 
    "Race" = "4. Race: Latino", 
    "Race" = "4. Race: Native", 
    "Race" = "4. Race: NHPI", 
    "Age" = "3. Age: 50-59", 
    "Age" = "3. Age: 60-69", 
    "Age" = "3. Age: 70+", 
    "Education" = "1. Education: Some College", 
    "Education" = "1. Education: College Graduate", 
    "Party ID" = "6. Party ID: Democrat", 
    "Party ID" = "6. Party ID: Independent", 
    "Party ID" = "6. Party ID: Other", 
    "Interaction" = "7. Interaction: Racial Belonging & Gender: Woman"
  )

  # Add the grouping variable to the data frame
  or_data_sig_renamed$group <- group_labels[rownames(or_data_sig_renamed)]

  # Reorder y-axis based on group labels (so they appear grouped and ordered)
  # or_data_sig_renamed$variable <- factor(rownames(or_data_sig_renamed), 
  #                                         levels = rownames(or_data_sig_renamed)[order(or_data_sig_renamed$OR)])
  #
